---
title: "Task2"
author: "Pavitra Desai"
date: "13/08/2021"
output:
   html_document:
     keep_md: yes
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# The Sparks Foundation - Data Science and Business Analytics 
### Task#2 : Prediction using Unsupervised Machine Learning 
### Problem Statement: From the given ‘Iris’ dataset, predict the optimum number of clusters and represent it visually.
**Importing necessary libraries**
```{r}
library(ggplot2)
library(gridExtra)
```
  
**Downloading and viewing Data**
```{r}
# data is readily available in RStudio "datasets" package
data(iris)
summary(iris)
head(iris)
dim(iris)
```
  
iris consist of 150 rows 5 columns    
**Preprocessing Data**
```{r}
is.null(iris)
any(is.na(iris))
data<-iris[,1:4]
species<-iris[,5]
head(data)
table(species)
```
  
iris is clean ie no null or na values .   
data is subset of iris with only needed columns.   
species shows original cluster having 50 values each.        
**Visualizing Data using Density Plot**
```{r}
plot1 <-    ggplot(iris, aes(x=Petal.Length, colour=Species, fill=Species)) +
  geom_density(alpha=0.5) +
  theme(legend.position="none")
plot2<- ggplot(iris, aes(x=Petal.Width, colour=Species, fill=Species)) +
  geom_density(alpha=0.5) +
  theme(legend.position="none")
plot3 <- ggplot(iris, aes(x=Sepal.Width, colour=Species, fill=Species)) +
  geom_density(alpha=0.5) +
  theme(legend.position="none")
plot4 <- ggplot(iris, aes(x=Sepal.Length, colour=Species, fill=Species))+
  geom_density(alpha=0.5) 
# Plot all density plots together
grid.arrange(plot1,plot2 ,plot3 ,plot4,nrow = 2
)
```
  
**Clustering Data using K-Means**   
k should be 3 because there are 3 different species    
Verifying using elbow method 
```{r}
wss <- sapply(1:10,function(k){kmeans(data, k, nstart=50,iter.max = 10)$tot.withinss})
plot(1:10, wss,type = "b")
```
    
   Verified k=3
```{r}
set.seed(120)
k3<-kmeans(data,3)
k3
#Comparing the predicted clusters with the original Clusters.
table(k3$cluster, iris$Species)
```
  
**Visualizing result**
```{r}
plota<-ggplot(iris, aes(x = Sepal.Length , y = Sepal.Width)) + 
  geom_point(aes(color = as.factor(k3$cluster))) +
  scale_color_discrete(name = " ", breaks=c("1", "2", "3"),labels=c("Sentosa", "virginica","versicolor")) +
  ggtitle("Cluster")
plotb<-ggplot(data=iris, aes(x =Sepal.Length , y = Sepal.Width)) +
  geom_point(aes(color=Species)) +
  ggtitle("Original")
plotc<-ggplot(iris, aes(x = Petal.Length , y = Petal.Width)) + 
  geom_point(aes(color = as.factor(k3$cluster))) +
  scale_color_discrete(name = " ", breaks=c("1", "2", "3"),labels=c("Sentosa", "virginica","versicolor")) +
  ggtitle("Cluster")
plotd<-ggplot(data=iris, aes(x =Petal.Length , y = Petal.Width)) +
  geom_point(aes(color=Species)) +
  ggtitle("Original")
grid.arrange(plota,plotb,plotc,plotd,nrow=2)
```
  
The plots are almost similar except for a few outliers.
  
# Thank You